---
title: "Lab 1: Social Network"
author: Justin Singh-Mohudpur
---

```{r setup, include=FALSE}
library(leaflet)

knitr::opts_chunk$set(
    "cache" = TRUE,
    "message" = FALSE,
    "warning" = FALSE
)
```

This dataset contains information about the American Mafia.
The data was collected by Dan DellaPosta at Penn State,
and it should **only** be used for this lab.

## Datasets
```{r datasets}
mafia_edges <- read.csv("labs/Lab1_mafi/MafiaEdges_2.csv", header = TRUE)
mafia_nodes <- read.csv("labs/Lab1_mafi/MafiaNodes_2.csv", header = TRUE)
```

### Mafia Edges
```{r show_edges, echo=FALSE}
knitr::kable(head(mafia_edges))
```

### Mafia Nodes
```{r show_nodes, echo=FALSE}
knitr::kable(head(mafia_nodes))
```

### Analysis
```{r mafia_graph}
g <- igraph::graph_from_edgelist(
    as.matrix(mafia_edges[, -3]),
    directed = "false"
)
```

Based on the above samples, we can notice a few things about this dataset:

- The network is **undirected**.
- The network is **unweighted**.
- The names of members are nodes.
- The network has the following characteristics:
    - `r nrow(mafia_edges)` edges.
    - `r nrow(mafia_nodes)` nodes.
    - density of `r igraph::edge_density(g)`
    - global clustering coefficient of `r igraph::global_efficiency(g)`
    - diameter of `r igraph::diameter(g)`
    - average path length of `r igraph::average.path.length(g)`

### Visualization
```{r mafia_sfnetwork}
mafia_sfnodes <- sf::st_as_sf(
    mafia_nodes,
    coords = c("LonX", "LatY"),
    crs = "EPSG:4326"
)

centrality <- igraph::eigen_centrality(g)$vector
ordering <- match(mafia_sfnodes$ID, names(centrality))
mafia_sfnodes$centrality <- centrality[ordering]

mafia_sfedges <- mafia_edges |>
    dplyr::left_join(
        dplyr::select(
            mafia_nodes,
            Source = ID,
            sx = LonX,
            sy = LatY
        )
    ) |>
    dplyr::left_join(
        dplyr::select(
            mafia_nodes,
            Target = ID,
            tx = LonX,
            ty = LatY
        )
    ) |>
    dplyr::select(from = Source, to = Target) |>
    dplyr::as_tibble()

mafia_network <- sfnetworks::sfnetwork(
    nodes = mafia_sfnodes,
    edges = mafia_sfedges,
    directed = FALSE,
    node_key = "ID",
    edges_as_lines = TRUE
)
```

```{r mafiaPlot}
leaflet::leaflet() |>
    leaflet::addTiles() |>
    leafgl::addGlPolylines(
        data = sf::st_as_sf(mafia_network, "edges"),
        opacity = 0.8,
        color = cbind(0, 0, 0),
        weight = 0.5
    ) |>
    leafgl::addGlPoints(
        data = sf::st_as_sf(mafia_network, "nodes"),
        radius = mafia_sfnodes$centrality * 20,
        popup = paste0(mafia_nodes$Label, " (", mafia_nodes$Family, ")")
    )
```